---
title: "Final_Writeup_STA523: LetMeIn"
author: "YHXLCLWYEL"
date: "12/12/2017"
output: html_document
runtime: shiny
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rvest)
library(magrittr)
library(stringr)
library(tibble)
library(tidyr)
library(dplyr)
library(purrr)
library(readr)
library(shiny)
library(shinydashboard)
library(gridExtra)
library(ggplot2)
```

## Overview of LetMeIn
LetMeIn is a ShinyApp that allows prospective students who want to apply to statistics graduate programs make better and faster decisions about where to apply based on their GPA, GRE scores and citizenship status. Students first select a school they are interested in, and LetMeIn calculates the average scores for accepted, rejected and waitlisted students and compares them to the student's scores. By seeing how their scores stack up, students can quickly determine whether they should apply to their selected school. All estimates are based on entries from thegradcafe.com, a public forum where graduate school applicants share their admissions information and whether they got accepted, rejected or waitlisted. 

This markdown explains the step-by-step process of creating LetMeIn. 

The process included the following steps: 
1) Scraping the appropriate data on statistics graduate programs from thegradcafe.com to put into a dataframe
2) Cleaning GRE scores in the dataframe
3) Cleaning the institution names to standarize them in the dataframe
4) Scraping Wikipedia for college descriptions and pictures for logos and seals
5) Generating the ShinyApp using the finalized dataframe from Step 3. 

## Step 1) Scrape data off of thegradcafe.com 

To create a dataframe including the institution name, program, degree, semester applied, student, application status, method of application, date of notification, GPA, and GRE scores, we initiated a dataframe called gradcafe. Next, we scraped the aforementioned elements from thegradcafe.com by identifying them through the selector gadget tool. The data was scraped column by column, splited into different pieces of information, and then stored into `institution`,`prog_date`, `program`, `degree`, `semester` and `decision`.  Then we used regular expressions to clean the outputs, filtered out the unrecognizable characters, and combined all the columns into one `.Rdata` file called `gradcafe.Rdata`. Moreover, we configured the gradcafe dataframe into a tidy format.

```{r , warning=FALSE, echo = FALSE, message=FALSE}
## Initiate data frame
gradcafe = data.frame(matrix(ncol = 13, nrow = 0))
colnames(gradcafe) = c("institution", "program", "degree","semester","student",
                       "status", "method", "date", "GPA", "GRE_Subject", "GRE_General_V",
                       "GRE_General_Q", "GRE_General_W")

## Scrape fro thegradcafe.com
for(i in 1:19) {
  url = paste("http://thegradcafe.com/survey/index.php?q=statistics&t=a&pp=250&o=&p=",i, sep="")
  page = read_html(url)
  institution = page %>% 
    html_nodes('.instcol') %>% 
    html_text()%>%
    str_replace("^\\s+","") %>% 
    {.[-1]}
  prog_date = page %>% 
    html_nodes(".instcol+ td") %>% 
    html_text() %>% 
    {.[-1]}
  program = prog_date %>% 
    str_extract("^[\\s,\\S]+,") %>% 
    str_replace_all(",","")
  degree = prog_date %>% 
    str_extract("Masters|PhD") %>% 
    str_extract("\\w+") %>% 
    ifelse(is.na(.), "Other",.)
  semester = prog_date %>% 
    str_extract("(\\S+)$") %>% 
    str_extract("\\w+")
  
  decision = page %>% 
    html_nodes('td:nth-child(3)') %>% 
    html_text() %>%
    {.[-1]} %>%
    str_split("(\\ via\\ |\\ on\\ |\\ Undergrad GPA:\\ |GRE General \\(V/Q/W\\):\\ |GRE Subject:\\ )")
  
  n.obs = sapply(decision, length)
  seq.max = seq_len(max(n.obs))
  mat = t(sapply(decision, "[", i = seq.max)) %>%
    as.data.frame(stringsAsFactors  = FALSE) %>%
    setNames(c("status", "method", "date", "GPA", "GRE_General", "GRE_Subject")) %>%
    mutate(GPA = as.numeric(GPA)) %>%
    mutate(GRE_Subject = as.numeric(str_replace(GRE_Subject, "♦","")))%>%
    mutate(GRE_General_V = as.numeric(substring(GRE_General,1,3))) %>%
    mutate(GRE_General_Q = as.numeric(substring(GRE_General,5,7))) %>%
    mutate(GRE_General_W = as.numeric(substring(GRE_General,9,12))) %>% 
    mutate(GRE_General = NULL) %>% 
    mutate(date = as.Date(date, format = "%d %b %Y"))
  
  student = page%>%
    html_nodes('td:nth-child(4)') %>%
    html_text() %>%
    {.[-1]} %>% 
    recode("A" = "American", "U" = "International with US degree", 
           "I" = "International without US degree",
           "O" = "Other", "?" = "Unknown") %>% 
    ifelse(.=="", "Unknown",.)
  
  temp = bind_cols(institution = institution, program = program, degree = degree,
                   semester=semester, student=student) %>% 
    bind_cols(mat)
  gradcafe = bind_rows(gradcafe,temp)
}

## Filter out spring applications 
## & applications before 2012 or after 2018
gradcafe = gradcafe %>%
  filter(!str_detect(semester,"12|S|18"))
levels(gradcafe$semester) = sapply(c(13:17), function(x) c(paste0("F",x)))

## Save scraped data to gradcafe.Rdata
save(gradcafe, file = "gradcafe.Rdata")
```

## Step 2) Convert the GRE scores 

In some of the older posts, the GRE scores were in an outdated scale:200-800. In order to analyze them together with the new GRE scores, we converted the old GRE scores in the dataset to match the new scoring scale used today based on the 'convert table' from ETS.  

```{r , warning=FALSE, echo = FALSE, message=FALSE}
gre_score = data.frame(prior = seq(800,200,-10),
           current = c(rep(170,5),rep(169,2),rep(168,2),167,166,rep(165,2),rep(164,2),
                       163,rep(162,2),161,rep(160,2),159,rep(158,2),157,rep(156,2),155,
                       rep(154,2),153,rep(152,2),rep(151,2),150,rep(149,2),148,147,
                       rep(146,2),145,144,rep(143,2),142,141,140,139,138,137,135,134,133,132,
                       131,rep(130,4)))

gre = vector()

for(i in seq_along(gre_score$prior)){
  gre[gre_score$prior[i]] = gre_score$current[i]
}

save(gre, file = "gre_score.Rdata")
```

## Step 3) Clean the institution names and gre scores

Next, we cleaned up the institution names to standardize them. (For example, the Georgia Institute of Technology could have been referred to as GA Tech.) 

To clean the GRE scores, we set up conditions to omit out-of-range scores in `gradcafe.Rdata`.

To clean the institution names, we created a csv file including all the keywords for each institution to detect and rename the same schools under a standardized name. The `School Names - Sheet1.csv` file is a google spreadsheet that contains the names of the most common schools in the gradcafe dataset in one column and all the key words we used to detect their names in a subsequent column. The schools in our csv files cover the top 75 statistics programs declared by US_news, as well as some other popular schools that we found in the gradcafe dataset.

We then scraped the US_news top Statistics programs and obtained the college names, locations, rank and average scores. The final results are stored in `us_news.R`, which helped us clean the institution names.

Next, we used keyword detection to match institution names in `gradcafe.Rdata` to  standardize their names in the csv file and `us_news.R`. Since many of the posts contains spelling errors, we also tried to capture some of the most commonly mispelled school names such as the word 'university'.

```{r, warning=FALSE, echo = FALSE, message=FALSE}
###########institution names
institution = read_csv("School Names - Sheet1.csv", col_names = FALSE)
names(institution) = c("standard", "abbr")
institution = institution %>%
  mutate(
    abbr = str_replace_all(abbr, "\"", ""),
    standard = str_replace_all(standard, "\"", "")) %>% 
  mutate(standard = str_replace_all(standard, "\\[\\d+\\] ","")) %>% 
  mutate(abbr = str_split(abbr, ","))

inst = data.frame(standard = rep(institution$standard, sapply(institution$abbr, length)), 
                  abbr = unlist(institution$abbr)) %>%
  mutate(standard = as.character(standard)) %>%
  mutate(abbr = toupper(abbr)) %>%
  mutate(abbr = str_trim(abbr))

###########clean columns except institution
load(file = "gradcafe.Rdata")
load(file = "gre_score.Rdata")

cleaned_gradcafe = gradcafe %>%
  mutate(GRE_Subject = ifelse(GRE_Subject < 100, GRE_Subject*10, GRE_Subject)) %>%
  mutate(GRE_General_V = ifelse(GRE_General_V < 200, GRE_General_V, gre[GRE_General_V])) %>%
  mutate(GRE_General_Q = ifelse(GRE_General_Q < 200, GRE_General_Q, gre[GRE_General_Q])) %>%
  mutate(GRE_General_V = ifelse(GRE_General_V < 130, NA, GRE_General_V)) %>%
  mutate(GRE_General_Q = ifelse(GRE_General_Q < 130, NA, GRE_General_Q)) %>%
  mutate(GRE_General_W = ifelse(GRE_General_W == 0, NA, GRE_General_W)) %>%
  mutate(GRE_General_W = ifelse(GRE_General_W < 1 & GRE_General_W > 0, GRE_General_W*10, GRE_General_W)) %>%
  filter(GPA <= 4 | is.na(GPA)) %>%
  filter(GRE_General_V <= 170 | is.na(GRE_General_V)) %>%
  filter(GRE_General_Q <= 170 | is.na(GRE_General_Q)) %>%
  filter(GRE_General_W <= 6 | is.na(GRE_General_W))

##########clean institution
cleaned_gradcafe = cleaned_gradcafe %>%
  mutate(institution = toupper(institution)) %>%
  mutate(institution = str_replace_all(institution, "  ", " ")) %>%
  mutate(institution = str_replace_all(institution, 
         "(UIVERSITY|UNIVERSTY|UNIVERISTY|UNIVERCITY|UNIVERSIY|
         UNIVERITY|UNIVERSEITY|UNIVERISITY|UNIERSITY|UNIVERAITY|
         UNIEVRSITY|UNVERSITY|UNVIERSITY|UNIVESITY)", "UNIVERSITY")) %>%
  filter(!str_detect(institution, "BRITISH")) %>%
  mutate(indicator = sapply(institution, function(x) which(str_detect(x,inst$abbr)))) %>%
  mutate(indicator = sapply(indicator, function(x) ifelse(length(x)==0, NA, min(x)))) %>%
  mutate(standard = ifelse(is.na(indicator), NA, inst$standard[indicator]))

cleaned_gradcafe = cleaned_gradcafe %>% drop_na(standard)

save(cleaned_gradcafe, file = "cleaned_gradcafe.Rdata")
```

## Step 4) Scrape Wikipedia for college descriptions and pictures for logos and seals

To include descriptions, logos and seals of the different colleges, we scraped Wikipedia for each college listed in the `cleaned_gradcafe.Rdata`

By pasting college names to the base url of Wikipedia webpage, we scraped the introduction paragraph from the Wikipage of each college. We also extracted the pictures, logos, and seals of that college from the same webpage. We used the selector gadget to identify nodes for each part, then cleaned them with regular expressions. We ended up with a list of introductions, pictures, logos and seals for each school. The results were stored as `wiki.Rdata`. 

```{r, echo = FALSE, message=FALSE, warning=FALSE}
load("cleaned_gradcafe.Rdata")
college_list = cleaned_gradcafe %>% 
  dplyr::select(standard) %>% unique() %>%  
  arrange((standard)) %>% 
  unname() %>% unlist()

base = "https://en.wikipedia.org/wiki/"

wiki = data.frame(matrix(ncol = 4, nrow = 0))
colnames(wiki) = c("college", "introduction", "seal_url", "logo_url")

for(i in 1:length(college_list)){
  college = str_replace_all(college_list[i],"--|—", ", ")
  college = str_replace_all(college," ", "_")
  url = paste0(base, college)
  page = read_html(url)
  
  ## Get introduction
  intro = page %>% html_nodes(".vcard+ p") %>% 
    html_text() %>% 
    str_replace_all("\\[\\d+\\]","") %>% 
    {.[1]}
  if(is.na(intro)){
    intro = page %>% html_nodes(".noviewer+ p")  %>% 
      html_text() %>% 
      str_replace_all("\\[\\d+\\]","") %>% 
      {.[1]}
  }
  if(is.na(intro)){
    intro = page %>% html_nodes(".tright+ p")  %>% 
      html_text() %>% 
      str_replace_all("\\[\\d+\\]","") %>% 
      {.[1]}
  }
  if(str_detect(intro, "^Coordinates")){
    intro = page %>% html_nodes("p:nth-child(4) , p:nth-child(3)")  %>% 
      html_text() %>% 
      str_replace_all("\\[\\d+\\]","") %>% 
      paste(., collapse = " ")
  }
  
  ## picture
  picUrl1 = page %>% html_nodes(".image img") %>% {.[1]} %>% 
    str_extract('src="[\\s,\\S]+?"') %>% 
    str_extract('//[\\s,\\S]+.[a-z]+')
  
  picUrl2 = page %>% html_nodes(".image img") %>% {.[2]} %>% 
    str_extract('src="[\\s,\\S]+?"') %>% 
    str_extract('//[\\s,\\S]+.[a-z]+')
  
  temp = bind_cols(college = college_list[i], introduction = intro,
                   seal_url = picUrl1, logo_url=picUrl2) 
  wiki = bind_rows(wiki,temp)
}

save(wiki, file = "wiki.Rdata")
```


## Step 5) Generate the ShinyApp and Discussion 

We created a ShinyApp to configure the data from gradcafe.com into an interactive interface. We added an introduction portion in the app in order to have a brief summary about the university. The app was built with the `shinydashboard` package.

The user interface includes following features:
i. a drop-down menu of a list of institutions from `cleaned_gradcafe.Rdata`
ii. a drop-down menu of programs including two options: `PhD` and `Masters`
iii. a check box: 'Provide Your Scores?': If checked, four slidebars will appear for users to input their own GPA, and GRE Verbal/Math/Writing scores.
iv. a check box: 'Specify Student Type?': If checked, users can see the results of only American students, international students or international students with US degrees. 
v. introduction button: if clicked, the introduction for the specified school will be displayed.

The main panel will output the following information:
i. Boxplots, lineplots and tables for GPA and GRE V/M/Q scores
ii. Enrollment rates for students who were accepted, rejected, and waitlisted
iii. Statistics for GRE subject test results


Discussion:
The app showed some interesting findings. We found that different schools focused on different scores. Harvard, for example, seems to prefer students with high GRE verbal and writing scores. On the contrary, Duke focuses more on quantitative scores.
Furthermore, American students usually have higher acceptance rates than international students. However, this may be due to the fact that there are much more international students who apply for graduate statistics programs than American students.

Limitations: 
Even though we have over 4000 data entries, there is insufficient data for some of the colleges. Therefore, it's difficult to run statistical analysis for these schools or draw general conclusions. As more and more posts appear on thegradcafe.com, our app will become increasingly helpful.  

```{r, echo = FALSE, message=FALSE, warning=FALSE}
load("cleaned_gradcafe.Rdata")
load("wiki.Rdata")

##########get function
get_data = function(this_school, this_degree, 
                    this_student = c("American", "International with US degree", 
                                     "International without US degree")) {
  result = cleaned_gradcafe %>%
    filter(standard == this_school) %>%
    filter(degree == this_degree) %>%
    filter(student %in% this_student) %>%
    filter(status != "Interview")%>%
    filter(status != "Other")
  
  
  return(result)
}

## List of colleges
college_list = cleaned_gradcafe %>% 
  dplyr::select(standard) %>% unique() %>%  
  arrange((standard)) %>% 
  unname() %>% unlist()

## List of student types
stu_type_list = cleaned_gradcafe %>% 
  dplyr::select(student) %>% unique() %>%  
  arrange((student)) %>% unname() %>% unlist() %>% {.[1:3]}

## Body
body <- dashboardBody(
  tabItems(
    tabItem(tabName = "databoard",
            ## Row1: info boxes
            h4("Enrollment Rates:"),
            fluidRow(
              infoBoxOutput("acceptRateBox"),
              infoBoxOutput("waitRateBox"),
              infoBoxOutput("totalBox")
            ),
            
            h4("GRE Subject Test:"),
            fluidRow(
              infoBoxOutput("participantsBox"),
              infoBoxOutput("avgScoreBox"),
              infoBoxOutput("rangeScoreBox")
            ),
            
            ## Row2: 2 tabboxes
            fluidRow(
              tabBox(
                title = tagList(shiny::icon("graduation-cap"), "GPA"),
                selected = "Boxplot",
                # The id lets us use input$tabset1 on the server to find the current tab
                id = "tabset1", height = "320px",
                tabPanel("Boxplot",
                         uiOutput("GPA")),
                tabPanel("Lineplot",
                         uiOutput("GPA_l")),
                tabPanel("Table", 
                         tableOutput("GPA_summary"))
              ),
              tabBox(
                title = tagList(shiny::icon("language"), "GRE Verbal"),
                selected = "Boxplot",
                height = "320px",
                tabPanel("Boxplot",
                         uiOutput("GRE_V")),
                tabPanel("Lineplot", 
                         uiOutput("GRE_V_l")),
                tabPanel("Table",
                         tableOutput("GRE_V_summary"))
              )
            ),
            
            ## Row3, 2 tabboxes
            fluidRow(
              tabBox(
                title = tagList(shiny::icon("cubes"), "GRE Quantitative"),
                selected = "Boxplot",
                height = "320px",
                tabPanel("Boxplot",
                         uiOutput("GRE_Q")),
                tabPanel("Lineplot",
                         uiOutput("GRE_Q_l")),
                tabPanel("Table",
                         tableOutput("GRE_Q_summary"))
              ),
              tabBox(
                title = tagList(shiny::icon("envelope-open"), "GRE Writing"),
                selected = "Boxplot",
                height = "320px",
                tabPanel("Boxplot",
                         uiOutput("GRE_W")),
                tabPanel("Lineplot",
                         uiOutput("GRE_W_l")),
                tabPanel("Table",
                         tableOutput("GRE_W_summary"))
              )
            )
    ),
    tabItem(tabName = "university",
            h2("University Introduction"),
            br(),
            uiOutput('logo'),
            br(),
            htmlOutput('name'),
            br(),
            htmlOutput('text'),
            br(),
            uiOutput('seal')
    )
  )
)

ui <- dashboardPage(
  dashboardHeader(title = "College Application"),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Databoard", tabName = "databoard", icon = icon("th")),
      menuItem("Introduction", icon = icon("envelope-o"), tabName = "university"),
      
      ## school input
      selectInput("school", label = h4("Universities"), 
                  choices = college_list, selected = "Duke University"),
      
      ## program input
      selectInput("program", label = ("Program"), 
                  choices = list("Masters", "PhD"), selected = "Masters"),
      
      ## scores input
      checkboxInput("scores","Provide Your Scores?", value = FALSE),
      conditionalPanel(
        "input.scores == true",
        sliderInput("gpa", "GPA", min=1, max=4, value=1,step=0.1),
        # numericInput("gpa", "GPA", value=0, min=1, max=4),
        sliderInput("grev", "GRE Verbal", min=130, max=170, value=130,step=1),
        # numericInput("grev", "GRE Verbal", value=0, min=130, max=170),
        sliderInput("greq", "GRE Math", min=130, max=170, value=130,step=1),
        # numericInput("greq", "GRE Math", value=0, min=130, max=170),
        sliderInput("grew", "GRE Writing", min=1, max=6, value=1,step=0.5)
        # numericInput("grew", "GRE Writing", value=0, min=1, max=6)
      ),
      
      ## stu_type input
      checkboxInput("is_type","Specify Student type?", value = FALSE),
      conditionalPanel(
        "input.is_type == true",
        selectInput("stu_type", label = ("Student type"), 
                    choices = stu_type_list, selected = "American")
      ),
      
      ## action buttion
      actionButton("find", "Show Magic")
      
    )
  ),
  body
)

server <- function(input, output) {
  output$participantsBox <- renderInfoBox({
    infoBox(
      "Participants:", "--%", 
      icon = icon("id-card-o"), color = "light-blue"
    )
  })
  
  output$avgScoreBox <- renderInfoBox({
    infoBox(
      "Average Score:", "--", 
      icon = icon("institution"), color = "light-blue"
    )
  })
  
  output$rangeScoreBox <- renderInfoBox({
    infoBox(
      "Score Range:", "-- to --", 
      icon = icon("database"), color = "light-blue"
    )
  })
  
  output$acceptRateBox <- renderInfoBox({
    infoBox(
      "Accept Rate:", "--%", 
      icon = icon("trophy"), color = "light-blue"
    )
  })
  
  output$waitRateBox <- renderInfoBox({
    infoBox(
      "Waitlist Rate:", "--%", 
      icon = icon("question"), color = "light-blue"
    )
  })
  
  output$totalBox <- renderInfoBox({
    infoBox(
      "Applicants Provided:", "--", 
      icon = icon("users"), color = "light-blue"
    )
  })
  
  
  observeEvent(input$find, {
    
    ## Get Dataset
    if(input$is_type){
      data = get_data(input$school, input$program, input$stu_type)
    }else{
      data = get_data(input$school, input$program)
    }
    
    
    ## Boxplots
    p1 = ggplot(data %>% filter(!is.na(GPA)), 
                aes(x = as.factor(status), y = GPA, fill = as.factor(status)))+
      geom_boxplot()+
      xlab("Status")+
      ylab("GPA")+
      scale_fill_manual(values=c("lightpink", "lightblue", "lightgrey"))+
      theme_bw()+
      guides(fill=guide_legend(title="Status"))
    
    p2 = ggplot(data %>% filter(!is.na(GRE_General_V)), 
                aes(x = as.factor(status), y = GRE_General_V, fill = as.factor(status)))+
      geom_boxplot()+
      xlab("Status")+
      ylab("GRE General Verbal")+
      scale_fill_manual(values=c("lightpink", "lightblue", "lightgrey"))+
      guides(fill=guide_legend(title=NULL))+
      theme_bw()
    
    p3 = ggplot(data %>% filter(!is.na(GRE_General_Q)), 
                aes(x = as.factor(status), y = GRE_General_Q, fill = as.factor(status)))+
      geom_boxplot()+
      xlab("Status")+
      ylab("GRE General Quantitative")+
      scale_fill_manual(values=c("lightpink", "lightblue", "lightgrey"))+
      guides(fill=guide_legend(title=NULL))+
      theme_bw()
    
    p4 = ggplot(data %>% filter(!is.na(GRE_General_W)), 
                aes(x = as.factor(status), y = GRE_General_W, fill = as.factor(status)))+
      geom_boxplot()+
      xlab("Status")+
      ylab("GRE General Writing")+
      scale_fill_manual(values=c("lightpink", "lightblue", "lightgrey"))+
      guides(fill=guide_legend(title=NULL))+
      theme_bw()
    
    mean.dis = data %>% group_by(semester = as.factor(semester), status = as.factor(status)) %>%
      summarise(avg.gpa = mean(GPA, na.rm = TRUE),
                avg.grev = mean(GRE_General_V, na.rm=TRUE),
                avg.greq = mean(GRE_General_Q, na.rm=TRUE),
                avg.grew = mean(GRE_General_W, na.rm=TRUE)
      ) 
    
    ## Lineplots
    p5 = ggplot(mean.dis %>% filter(!is.na(avg.gpa)), 
                aes(x = semester, y = avg.gpa, color = status, group = status))+
      geom_line()+
      scale_color_manual(values=c("lightpink", "lightblue", "lightgrey"))+
      xlab("Semester")+
      ylab("Average GPA")+
      theme_bw()+
      guides(fill=guide_legend(title="Status"))
    
    p6 = ggplot(mean.dis %>% filter(!is.na(avg.grev)), 
                aes(x = semester, y = avg.grev, color = status, group = status))+
      geom_line()+
      scale_color_manual(values=c("lightpink", "lightblue", "lightgrey"))+
      xlab("Semester")+
      ylab("Average GRE Verbal")+
      theme_bw()+
      guides(fill=guide_legend(title="Status"))
    
    p7 = ggplot(mean.dis %>% filter(!is.na(avg.greq)), 
                aes(x = semester, y = avg.greq, color = status, group = status))+
      geom_line()+
      scale_color_manual(values=c("lightpink", "lightblue", "lightgrey"))+
      xlab("Semester")+
      ylab("Average GRE Quantitative")+
      theme_bw()+
      guides(fill=guide_legend(title="Status"))
    
    p8 = ggplot(mean.dis %>% filter(!is.na(avg.grew)), 
                aes(x = semester, y = avg.grew, color = status, group = status))+
      geom_line()+
      scale_color_manual(values=c("lightpink", "lightblue", "lightgrey"))+
      xlab("Semester")+
      ylab("Average GRE Writing")+
      theme_bw()+
      guides(fill=guide_legend(title="Status"))
    
    ## Add lines for "your score"
    if(input$scores){
      p1 = p1 + geom_hline(aes(yintercept=input$gpa), colour="#990000")
      p2 = p2 + geom_hline(aes(yintercept=input$grev), colour="#990000")
      p3 = p3 + geom_hline(aes(yintercept=input$greq), colour="#990000")
      p4 = p4 + geom_hline(aes(yintercept=input$grew), colour="#990000")
      p5 = p5 + geom_hline(aes(yintercept=input$gpa), colour="#990000")
      p6 = p6 + geom_hline(aes(yintercept=input$grev), colour="#990000")
      p7 = p7 + geom_hline(aes(yintercept=input$greq), colour="#990000")
      p8 = p8 + geom_hline(aes(yintercept=input$grew), colour="#990000")
    }
    
    ## Plot outputs
    
    output$GPA <- renderUI({
      if(nrow(data %>% filter(!is.na(GPA)))>0){
        output$myPlot_GPA <- renderPlot({
          p1
        })
        plotOutput("myPlot_GPA", height = "250px")  
      }else{
        img(src = "https://www.anychart.com/products/anychart/history/images/no-data-label.svg", height = "250px", align = "center")
      }
    })
    
    output$GRE_V <- renderUI({
      if(nrow(data %>% filter(!is.na(GPA)))>0){
        output$myPlot_GRE_V <- renderPlot({
          p2
        })
        plotOutput("myPlot_GRE_V", height = "250px")  
      }else{
        img(src = "https://www.anychart.com/products/anychart/history/images/no-data-label.svg", height = "250px", align = "center")
      }
    })
    
    output$GRE_Q <- renderUI({
      if(nrow(data %>% filter(!is.na(GPA)))>0){
        output$myPlot_GRE_Q <- renderPlot({
          p3
        })
        plotOutput("myPlot_GRE_Q", height = "250px")  
      }else{
        img(src = "https://www.anychart.com/products/anychart/history/images/no-data-label.svg", height = "250px", align = "center")
      }
    })
    
    output$GRE_W <- renderUI({
      if(nrow(data %>% filter(!is.na(GPA)))>0){
        output$myPlot_GRE_W <- renderPlot({
          p4
        })
        plotOutput("myPlot_GRE_W", height = "250px")  
      }else{
        img(src = "https://www.anychart.com/products/anychart/history/images/no-data-label.svg", height = "250px", align = "center")
      }
    })
    
    output$GPA_l <- renderUI({
      if(nrow(data %>% filter(!is.na(GPA)))>0){
        output$myPlot_GPA_l <- renderPlot({
          p5
        })
        plotOutput("myPlot_GPA_l", height = "250px")  
      }else{
        img(src = "https://www.anychart.com/products/anychart/history/images/no-data-label.svg", height = "250px", align = "center")
      }
    })
    
    output$GRE_V_l <- renderUI({
      if(nrow(data %>% filter(!is.na(GPA)))>0){
        output$myPlot_GRE_V_l <- renderPlot({
          p6
        })
        plotOutput("myPlot_GRE_V_l", height = "250px")  
      }else{
        img(src = "https://www.anychart.com/products/anychart/history/images/no-data-label.svg", height = "250px", align = "center")
      }
    })
    
    output$GRE_Q_l <- renderUI({
      if(nrow(data %>% filter(!is.na(GPA)))>0){
        output$myPlot_GRE_Q_l <- renderPlot({
          p7
        })
        plotOutput("myPlot_GRE_Q_l", height = "250px")  
      }else{
        img(src = "https://www.anychart.com/products/anychart/history/images/no-data-label.svg", height = "250px", align = "center")
      }
    })
    
    output$GRE_W_l <- renderUI({
      if(nrow(data %>% filter(!is.na(GPA)))>0){
        output$myPlot_GRE_W_l <- renderPlot({
          p8
        })
        plotOutput("myPlot_GRE_W_l", height = "250px")  
      }else{
        img(src = "https://www.anychart.com/products/anychart/history/images/no-data-label.svg", height = "250px", align = "center")
      }
    })
    
    output$GPA_summary <- renderTable(
      data %>% 
        group_by(status) %>%
        summarize(min = min(GPA, na.rm = TRUE), median = median(GPA, na.rm = TRUE), max = max(GPA, na.rm = TRUE)) %>%
        as.data.frame()
    )
    
    output$GRE_V_summary <- renderTable(
      data %>% 
        group_by(status) %>%
        summarize(min = min(GRE_General_V, na.rm = TRUE), median = median(GRE_General_V, na.rm = TRUE), max = max(GRE_General_V, na.rm = TRUE)) %>%
        as.data.frame()
    )
    
    output$GRE_Q_summary <- renderTable(
      data %>% 
        group_by(status) %>%
        summarize(min = min(GRE_General_Q, na.rm = TRUE), median = median(GRE_General_Q, na.rm = TRUE), max = max(GRE_General_Q, na.rm = TRUE)) %>%
        as.data.frame()
    )
    
    output$GRE_W_summary <- renderTable(
      data %>% 
        group_by(status) %>%
        summarize(min = min(GRE_General_W, na.rm = TRUE), median = median(GRE_General_W, na.rm = TRUE), max = max(GRE_General_W, na.rm = TRUE)) %>%
        as.data.frame()
    )
    
    ## Calculate Gre Subject participant rate, avg score, and accept rate
    total_df = cleaned_gradcafe %>% 
      filter(standard==input$school, degree==input$program)
    if(input$is_type){
      total_df = total_df %>% filter(student==input$stu_type)
    }
    greSubject = total_df %>% 
      filter(!is.na(GRE_Subject)) %>% 
      summarize(count = n(), avg = mean(GRE_Subject), 
                min_score = min(GRE_Subject), max_score = max(GRE_Subject))
    total_num = total_df %>% nrow()
    greSub_perc = round((greSubject$count)*100/total_num, digits=2)
    greSub_perc = ifelse(is.na(greSub_perc), "--", as.character(greSub_perc))
    greSub_score = ifelse(is.na(greSubject$avg), "--", 
                          as.character(round(greSubject$avg, digits=2)))
    greSub_min = ifelse(is.na(greSubject$min_score) | is.infinite(greSubject$min_score), "--", 
                        as.character(round(greSubject$min_score, digits=2)))
    greSub_max = ifelse(is.na(greSubject$max_score) | is.infinite(greSubject$max_score), "--", 
                        as.character(round(greSubject$max_score, digits=2)))
    accept_num = total_df %>% filter(status=="Accepted") %>% nrow()
    accept_rate = ifelse(is.na(accept_num/total_num), "--",
                         as.character(round(accept_num*100/total_num, digits=2)))
    wait_num = total_df %>% filter(status=="Wait listed") %>% nrow()
    wait_rate = ifelse(is.na(wait_num/total_num), "--",
                       as.character(round(wait_num*100/total_num, digits=2)))
    
    ## infoBox for Gre subject rate
    output$participantsBox <- renderInfoBox({
      infoBox(
        "Participants:", paste0(greSub_perc, "%"), 
        icon = icon("id-card-o"), color = "light-blue"
      )
    })
    
    ## info Box for Gre Subject score
    output$avgScoreBox <- renderInfoBox({
      infoBox(
        "Average Score:", greSub_score, 
        icon = icon("institution"), color = "light-blue"
      )
    })
    
    ## info Box for Gre Score Range
    output$rangeScoreBox <- renderInfoBox({
      infoBox(
        "Score Range:", paste0(greSub_min, " to ", greSub_max), 
        icon = icon("database"), color = "light-blue"
      )
    })
    
    ## info Box for accept rate
    output$acceptRateBox <- renderInfoBox({
      infoBox(
        "Accept Rate:", paste0(accept_rate, "%"), 
        icon = icon("trophy"), color = "light-blue"
      )
    })
    
    ## info Box for waitlist rate
    output$waitRateBox <- renderInfoBox({
      infoBox(
        "Waitlist Rate:", paste0(wait_rate, "%"), 
        icon = icon("question"), color = "light-blue"
      )
    })
    
    ## info Box for total number
    output$totalBox <- renderInfoBox({
      infoBox(
        "Applicants Provided:", total_num, 
        icon = icon("users"), color = "light-blue"
      )
    })
    
    ## University Introduction
    intro = wiki %>% filter(college == input$school) %>% 
      select(introduction) %>% unname() %>% unlist()
    logo_url = wiki %>% filter(college == input$school) %>% 
      select(logo_url) %>% unname() %>% unlist()
    seal_url = wiki %>% filter(college == input$school) %>% 
      select(seal_url) %>% unname() %>% unlist()
    school_name = input$school
    output$name <- renderUI({
      h4(school_name)
    })
    output$text <- renderUI({
      HTML(intro)
    })
    output$logo <- renderUI({
      img(src = logo_url,
          align = "center")
    })
    output$seal <- renderUI({
      img(src = seal_url,
          align = "center")
    })
    
    
  },ignoreInit = TRUE)
}

shinyApp(ui, server)
```

